; -*- mode: conf-windows; coding: windows-1251-dos -*-
;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;	 ,,,,,      ,,,,,,,    ,,,,,,_  ,,,,,,,,  ,,,,,,   
;       MMMMM1     M0MMMM&    MMMMM@'  MMMMMM0"  MMMM0!   
;       4MMMM#      ^MMMMMr   MMMMMf    #MMMM&    B0'     
;      &]MMMMMc      #MMMM# ] MMMMMf    #MMMM&   j#       
;      M 0MMMM&       MMMMML# MMMMMf    #MMMM&  pM&       
;     pY 4MMMMM     ] #MMMMM# MMMMMf    #MMMM& pMMMt      
;     M   MMMMMc    ]& MMMMMf MMMMMf    #MMMM&]MMMM0      
;    ]#   0MMMM&    ]M #MMMM  MMMMMf    #MMMM& MMMMM&     
;    QfjMMMMMMMM    ]M  MMMf  MMMMMf    #MMMM& 4MMMMM     
;   _M    "MMMMMf   ]M  BMM   MMMMMf    #MMMM&  MMMMM&    
;  _Q#     MMMMM&   jMg  M8  _MMMMMf    BMMMM&  jMMMMM,   
; 4MMMM   #MMMMMM# 0MMM& B  ]MMMMMMM&  0MMMMMM&]MMMMMMMt  
;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;

;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;;Скальп Контролера 
;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;

[af_armor_4]:af_base
GroupControlSection	= spawn_group
$spawn 			= "artifacts\dummy pellicle"
$npc			= on				; option for Level Editor
;$prefetch 		= 3
cform           = skeleton
class   		= ARTEFACT

visual				= physics\anomaly\artefact_plenka1.ogf
description			= enc_zone_artifact_armor_4
inv_name			= af_armor_4
inv_name_short		= 
inv_weight			= 2.0

inv_grid_x			= 7
inv_grid_y			= 38

jump_height			= 1

cost				= 20000	;200

particles			= anomaly2\artefact\artefact_ameba




lights_enabled = true	;true			;???? ?????? 
trail_light_color = 0, 107, 0  
trail_light_range = 2


;скорости увеличения (уменьшения) 
health_restore_speed		= 0.0			
radiation_restore_speed		= 0.001 ;+10
satiety_restore_speed		= -0.00011		
power_restore_speed		= 0.0		
bleeding_restore_speed		= 0.0
hit_absorbation_sect		= af_armor_4_absorbation

artefact_activation_seq		= af_activation_bold
art_hit.art_hit = 0.8, 0.3, telepatic

[af_armor_4_absorbation]
burn_immunity = 0.72				;коэффициенты иммунитета 
strike_immunity = 1.0
shock_immunity = 1.0
wound_immunity = 1.0		
radiation_immunity = 1.0
telepatic_immunity = 0.6
chemical_burn_immunity = 0.85
explosion_immunity = 1.0
fire_wound_immunity  = 1.0


;                                                                                                 
 ;        `/            `.`/y                                                                        
  ;      `yM:           hNNMo                                       `d`                              
   ;     hMMN          oMMMM.                                   -dyshMo                              
    ;    hMMN         .MMMMs                               `mNhomMMMMMs                              
     ;   hMMm         sMMMm`                              `yMMMMMMMMMMs                              
    ;    hMMd       `yMMMM:                            .sdMMMMMMMMMMMMy                              
   ;    `dMMm.     `dMMMMo                             yMMMMMMmysyMMMMy                              
  ;     /MMMMy `-``dMMMN:                             .MMMMMMy   -MMMMs                              
 ;      `NMMMm /MMNMMMm.               -`             sMMMMd`    /MMMM+                              
;        hMMMM.-MMMMMN.                yMN+          `MMMMM/     /MMMM-                              
;        +MMMMydMMMMM:                 oMMMN.        sMMMMN`     :MMMM.                `/            
;        .MMMMMMMMMMh                  .mMMMm`      `NMMMMh      .MMMM.      `+:    :+syM/           
;         mMMMMMMMMMN.                :shMMMMy      oMMMMMy      `MMMM:     .MMh .+mMMMMMy           
;         yMMMMMMdNMMs              `hMMMMMMMM/     +MMMMMh       NMMMy    :NMMhyMMMMMMMMN`          
;         yMMMMy.`oMMN.            `mMMMMMdmMMN.    -MMMMMM`      mMMMd`  /NMMMMMMMMMMMMMM+          
;       -hMMMMM:  `mMMd`          .mMMMMs: +MMMh    `dMMMMMyoy - sMMMM:  oMMMMMMMMh-.dMMMMm          
;       dMMMMMM/   /MMMs          /MMMMm`  -MMMM+    `NMMMMMMMMMmMMMMM:  +NMMMMMMo   `yMMMM:         
;       yMmMMMMs    sMMMs         hMMM:     dMMMN     yMMMMMMMMMMMMMMM-   hMMMMMN`    `+MMMm/        
;       -- NMMMs     dMMMs       `NMMd      :MMMM.    ..+MMMMMMMmyMMMM`   hMMMMMy      .MMMMm        
;          mMMM+     oMMMM-      `MMMd       hMMM:      .NMMMm-.``MMMM-   dMMMMM+      -MMMMN        
;          NMMM/     -MMMMm      `MMMd       sMMM-     -mMMMN.    NMMM/  -MMMMm.       :MMMMM.       
;         `MMMM-      mMMMN      .MMMy`      oMMM.    :NMMMN-     mMMMo  /MMMMh        /MMMMM/       
;         .MMMM.      :NMMMs     .MMMMo     -NMMM`   /MMMMM:      hMMMN` +MMMMm        +MMMM-        
;         .MMMM`       oMMMM+    `MMMMd    `mMMMy   .NMMMM/       sMMMM- /MMMMN        /MMMM-        
;         `NMMM`       `NMMMM-    hMMMM-   oMMMM-   yMMMMo        -NMMM: oMMMMd         dMMM+        
;          :MMN`        +MMMMy    .dMMMN-`-mMMMd   /MMMMh          hMMM/ yMMMMs         sMMMy        
 ;         -MMN`        `NMMMMo`   `NMMMMMMMMMd:  .NMMMy`          dMMMo :MMMM+         oMMMd        
 ;         -MMM`         :NMMMMs    sMMMMMMMMN`  `mMMMo            NMMMs  mMMN.         oMMMN        
 ;         .MMM`          oMMMMN`   .yohMMMMM+   yMMMd             NMMMy  +N/.          `dMMM`       
 ;         `MMM.          .NMMMMy       .oss:   :MMMN-             sMMMs                 `sMd        
 ;          mMM.           :MMMMMs              mMMM+              -MMd`                   ..        
 ;          :Ms             dMMMMM.            /MMNs                NM/                              
 ;           -`             -MMMMMs            `Ny`                 .o.                              
 ;                           dMMMMM.           -+                                                    
 ;                           /NdMMM+                                                                 
 ;                            ` :hh                                                                  
 ;                                                                                                   
                                                                                                    
